### 2023-06-05 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
added reference
added a few more refs
adding some of the postprocessing docs

%\citet{yan-ima-tan2010} perform experiments with multicomponent GUVs. They observe phase separation and budding of vesicles with a small reduced volume. However, the budding often requires a significant amount of time (tens of minutes), but ours occur much earlier in the contracting example by using narrow constrictions. Equations (2)--(5) shows a model similar to ours, and they use a linear dependence between the bending modulus and lipid concentration in the paragraph immediately after these equations. The include an energy term that depends on the difference in area between the inner and outer monolayer of lipids. Osmotic gradients are used to control the vesicle volume.

>>>>

\citet{gur-pak-tay-siv-sac2023} look at the effect of membrane
viscoelasticity.

\citet{ram-kom-sek-ima2010}

\citet{che-lyu-jae-leo2020}

\citet{wan-ii-sug-nod-jin-liu-che-gon2023}

\citet{mis-wis-ber-key-li-tun-law-per-erd-zha-zha-sun-kal-lam-kon2019}
is paper with Sean Sun that looks at linear and non-linear shear in the
boundary layer caused by tank treading behavior.

%\citet{yan-ima-tan2010} perform experiments with multicomponent GUVs.
%They observe phase separation and budding of vesicles with a small
%reduced volume. However, the budding often requires a significant
%amount of time (tens of minutes), but ours occur much earlier in the
%contracting example by using narrow constrictions. Equations (2)--(5)
%shows a model similar to ours, and they use a linear dependence between
%the bending modulus and lipid concentration in the paragraph
%immediately after these equations. The include an energy term that
%depends on the difference in area between the inner and outer monolayer
%of lipids. Osmotic gradients are used to control the vesicle volume.
